%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%DAVID TSENTER PERSONAL RESUME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{DavidTsenterResume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{David}{Tsenter}{ \urlstyle{same}\url{http://davidtsenter.com} \\
\href{mailto:tsenterd@gmail.com}{tsenterd@gmail.com} | 416.358.7950
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Waterloo}
\descript{Accepted}
\descript{BSE in Software Engineering}
\location{Starting September 2015 | Waterloo,ON \\GPA: N/A}
\sectionsep

\subsection{W.L Mackenzie C.I}
\location{Grad. June 2015|  Toronto, ON}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Experienced With:}
\textbullet{}Java \textbullet{}   HTML\textbullet{}CSS \textbullet{} JavaScript\\ \textbullet{} C 
 \textbullet{} Python \textbullet{} PowerShell \textbullet{}Bash\textbullet{}Android \textbullet{} \LaTeX\ \\ 
 \vspace{2mm}
\location{Familiar With:}
Arduino \textbullet{} C++ \textbullet{} PHP \textbullet{} Assembly \\
MatLab \textbullet{} Node.js \ \textbullet{} MySQL
\sectionsep
\vspace{1mm}
\subsection{Tools}
\textbullet{} Git\textbullet{}Android Studio \textbullet{}Eclipse\\
\textbullet{}Active Directory \textbullet{}Windows Server  \\

\vspace{4mm}


%%%%%%%%%%%%%%%%%%%%%%%%
\section{Interests}
\textbullet{} Hackathons \\
\textbullet{} Entrepreneurship \\
\textbullet{} Competitive Programming \\
\textbullet{} Website Design \\
\textbullet{} Volunteering\\
\sectionsep
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/tsenterd}{\custombold{tsenterd}} \\
Twitter://  \href{https://twitter.com/TsenterDavid}{\custombold{@TsenterDavid}} \\
LinkedIn://  \href{https://www.linkedin.com/in/davidtsenter}{\custombold{davidtsenter}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Western Learning Academy}
\descript{| Head Tutor}
\location{November 2014 – Current | Toronto, ON}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Tutored students from grades 1 through college in a variety of subjects such as
math, physics, chemistry, and computer science.
\item In charge of newly opened location
\end{tightemize}
\sectionsep

\runsubsection{Kobo Inc.}
\descript{| Junior Systems Administrator }
\location{July - September 2013 | Toronto, ON}

\begin{tightemize}\item Developed and deployed the new user account automation script (Active Directory,Exchange) using Windows PowerShell
\item Assisted in Exchange server migration
\end{tightemize}
\sectionsep

\runsubsection{Kobo Inc.}
\descript{| IT Summer Intern }
\location{August - September 2012| Toronto, ON}
\begin{tightemize}
\item Performed Hardware and Software deployments/upgrades
\item Assisted remote and local employees with technical issues 
\item Developed and deployed domain computer encryption script

\end{tightemize}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{\href{https://github.com/tsenterd/DavidTsenterWebsite}{DavidTsenter.com}}
\descript{|My personal website}
\location{Dec 2014 – Present}
 \textbf{\href{http://davidtsenter.com}{My Website}} showcases all of my projects, provides a brief history of myself, and provides links to their respective github pages. Created using HTML, CSS, and PHP. Uses parallax and bootsrap.
\sectionsep

\runsubsection{\href{https://github.com/tsenterd/Speakeasy}{Speakeasy}}
\descript{| Voice Recognition based game}
\location{April 2013 – June 2013 | }
A Jave-based game created for my grade 12 computer science final project. It uses the CMU Sphinx API and teaches the user how to pronounciate simple English Phrases. I was the lead developer focusing on the voice recognition aspects. Co created with Alex Zvorygin.\\
\sectionsep

\runsubsection{\href{https://github.com/tsenterd/Kolingo}{Kolingo}}
\descript{| Teacher-student communication platform}
\location{November 2014}
Created during the Edapphack hackathon. I was lead developer for the android-version of the application. Assisted with the website. 
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%
\section{ExtraCurriculars}
\textbullet{} Hackathon President \\
\textbullet{} Computer Programming Team Vice President \\
\textbullet{} Filmmaker (Visual Effects) \\
\textbullet{} North York Food Harvest Volunteer \\
\sectionsep
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2015	     & 2nd place  & JDCC programming contest\\
2015     & Top 25 percent& CSMC Math Contest\\
2014	     & 18th in Ontario  & ECOO programming contest\\

\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
